---
title: "MCC simulations"
author: "Ethan Naegele"
date: "2024-07-29"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(knockoff)
library(pracma)
library(tidyverse)
library(TreeTools)
library(here)
library(foreach)
library(doParallel)
library(cknockoff)
```

LFL = Luo, Fithian, and Lei, referring to the authors of the "Improving knockoffs with conditional calibration" paper





# small scale - trying to get a rough calibration of the BH

we choose $\beta^*$ such that base BH with $\alpha = .20$ has power of about 35% for the setting. In some of the experiments below, we approximated the power to be 50%, but in the full scale simulation, the power ended up being 35%. 

## mcc


```{r}
set.seed(17)
run_bh_mcc_lfl_setting_simulation(a_vec = c(3.63), alpha = .2, num_iter = 200)
```

```{r}
set.seed(18)
run_bh_mcc_lfl_setting_simulation(a_vec = c(3.7, 3.8), alpha = .2, num_iter = 400)
```

```{r}
set.seed(19)
run_bh_mcc_lfl_setting_simulation(a_vec = c(3.75), alpha = .2, num_iter = 600)
```

```{r}
set.seed(20)
run_bh_mcc_lfl_setting_simulation(a_vec = c(3.73), alpha = .2, num_iter = 700)
```
```{r}
set.seed(21)
run_bh_mcc_lfl_setting_simulation(a_vec = c(3.7), alpha = .2, num_iter = 700)
```

```{r}
set.seed(22)
run_bh_mcc_lfl_setting_simulation(a_vec = c(3.68), alpha = .2, num_iter = 800)
```

```{r}
set.seed(23)
run_bh_mcc_lfl_setting_simulation(a_vec = c(3.67, 3.68), alpha = .2, num_iter = 1000)
```

```{r}
set.seed(23)
run_bh_mcc_lfl_setting_simulation(a_vec = c(3.67, 3.68), alpha = .2, num_iter = 1000)
```

```{r}
set.seed(25)
run_bh_mcc_lfl_setting_simulation(a_vec = c(3.66), alpha = .2, num_iter = 1000)
```

```{r}
set.seed(26)
run_bh_mcc_lfl_setting_simulation(a_vec = c(3.66), alpha = .2, num_iter = 1500)
```

```{r}
set.seed(27)
run_bh_mcc_lfl_setting_simulation(a_vec = c(3.66), alpha = .2, num_iter = 400)
```


mcc calibration is $\beta^* \approx 3.63$ for 35% power.

mcc calibration is $\beta^* \approx 3.66$ for 50% power.



## mcc block


```{r}
set.seed(20)
run_bh_mcc_lfl_setting_simulation(type = 'MCC_Block', a_vec = c(3.2), alpha = .2, num_iter = 300)
```


mcc block calibration is $\beta^* \approx 3.2$.



## IID normal

```{r}
set.seed(30)
run_bh_mcc_lfl_setting_simulation(type = 'IID_Normal', a_vec = c(.073), alpha = .2, num_iter = 1000)
```

for IID normal, we have $\beta^* \approx .073$. 


```{r}
set.seed(32)
run_bh_mcc_lfl_setting_simulation(type = 'IID_Normal', a_vec = c(.075), alpha = .2, num_iter = 1000)
```
```{r}
set.seed(32)
run_bh_mcc_lfl_setting_simulation(type = 'IID_Normal', a_vec = c(.08), alpha = .2, num_iter = 400)
```
```{r}
set.seed(33)
run_bh_mcc_lfl_setting_simulation(type = 'IID_Normal', a_vec = c(.083), alpha = .2, num_iter = 500)
```

```{r}
set.seed(34)
run_bh_mcc_lfl_setting_simulation(type = 'IID_Normal', a_vec = c(.083), alpha = .2, num_iter = 1000)
```

$\beta^* \approx .083$ to achieve about 50% power for IID Normal setting. 

## X_AR

```{r}
set.seed(31)
run_bh_mcc_lfl_setting_simulation(type = 'X_AR', a_vec = c(2.83), alpha = .2, num_iter = 1000)
```

for X_AR, we have $\beta^* \approx 2.83$. 
